Helmet Foam Case Study Report

### 2024-04-29 CS2 Final Draft.qmd
Update CS2 Final Draft.qmd
updated #1.2

Explanatory Variables:

@@

Aside from cycle, all of these explanatory variables are constant across all measurements of an individual foam piece.

Response Variables:

|    Variable Name    |                   Description                                       |
|:--------------------|:---------------------------------------------------------------------------------------------|
|     stiffness        |  measurement of the foam’s stiffness. (Originally labeled “E1_MPA”)|
|      damping         |  measurement of the foam’s damping. (Originally labeled “delta_rad”)|
|    stiffnessFrac     |  stiffness / first stiffness measurement|
|     dampingFrac      |  tan(damping) / tan(first damping measurement)

>>>>

**Explanatory Variables:**

@@

*Caption: Table 1. Explanatory Variables*

**Response Variables:**

|    Variable Name    |                   Description                                       |
|:--------------------|:---------------------------------------------------------------------------------------------|
|     stiffness        |  measurement of the foam’s stiffness. (Originally labeled “E1_MPA”)|
|      damping         |  measurement of the foam’s damping. (Originally labeled “delta_rad”)|
|    stiffnessFrac     |  stiffness / first stiffness measurement|
|     dampingFrac      |  tan(damping) / tan(first damping measurement)|

*Caption: Table 2. Response Variables*
